The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
not Vampire -> not by Vampire

Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018. After fixing this misinterpretation we note that only a single division winner changes - in 2017 AUFNIRA should have been won by CVC4 and not Vampire.

>>>>

Whilst producing these results we noticed that the description of what constitutes a family had been incorrectly interpreted by the scoring scripts in 2016-2018. After fixing this misinterpretation we note that only a single division winner changes---in 2017 AUFNIRA should have been won by CVC4 and not by Vampire.
